\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

% Title Info
\title{Want2Remember SDD}
\author{CS3338 Group 3: Joshua Hanscom, Nicholas Montales, Jessie Guijosa, Perla Reyes}
\date{20 November 2024}

% Page Layout
\geometry{a4paper, margin=1in}
\pagestyle{fancy}
\fancyhead[R]{Page \thepage}
\fancyfoot[R]{SDD}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section*{Version Description}
\begin{tabular}{|c|p{10cm}|c|}
\hline
\textbf{Version} & \textbf{Description of Changes} & \textbf{Date} \\ \hline
1.0 & Initial version of the Software Design Document. & 20 November 2024 \\ \hline
1.1 & Snapshot 1: Memory Home Page & 9 December 2024 \\ \hline
1.2 & Snapshot 2: Memory Creation Page & 9 December 2024 \\ \hline
1.3 & Snapshot 3: More Details Page & 10 December 2024 \\ \hline
1.4 & Snapshot 4: Memory Contact Page & 10 December 2024 \\ \hline
\end{tabular}
\newpage

\section{Introduction}
\subsection{Purpose of the Document}
Want2Remember is a web application that assists those with cognitive impairments in remembering day-to-day tasks and memories. The system keeps track of user-generated data, such as memories, to-do lists, appointments, contacts, and payment information. This document explains the functionality, design, architecture, and requirements of the Want2Remember application.

\subsection{Intended Audience}
This document is intended for the California State University of Los Angeles (CSULA) Computer Science department. It is part of the Senior Design Project sponsored by We2Link. The audience includes professors, students of CSULA, and employees of We2Link.

\subsection{Overview of the System}
Want2Remember uses a component-based architecture to enhance reusability and reduce the size and complexity of the codebase.

\section{System Architecture}
\subsection{Workflow of the System}
The Want2Remember app allows users to store and create memories while enabling caregivers to provide support. User data is stored in Firebase. Users can create and edit memories, which are synchronized in real-time with Firebase. Caregivers can also interact with the app to assist users.

\subsection{System Components}
\textbf{Client-Side:} 
The client side uses React for the web interface and React Native for the mobile app. Tailwind CSS ensures responsive and consistent styling. Key screens include:
\begin{description}
\item[Caregivers screen:] Displays caregiver information and access.
\item[Memories Creation Page:] Allows the user to create Memory tiles in order to save information that they could forget. There should also be a longer description that can be attached to every memory tile. The information should also be able to be viewed by clicking the memory tile.
\item[Contact Memory Creation Page:] Allows the user to create Memory tiles in order to save contact information that they could forget. There should also be a longer description that can be attached to every contact memory tile. The information should also be able to be viewed by clicking the contact memory tile.
\item[Account screen:] Allows users to manage settings.
\end{description} details (e.g., category, date, location).

\textbf{Server-Side:} 
Firebase serves as the backend, providing real-time data storage and synchronization. Firebase Authentication ensures secure user access. React JS components handle interactions with Firebase, ensuring seamless updates.

\section{User Interface}
\subsection{How to Use the System}
Users interact through various screens, including login, dashboard, and memory creation. Real-time data updates are stored in Firestore. Features include filtering and searching memories by category, type, and timeframe.

\subsection{Database Design}
The app utilizes Firestore, organizing data into collections for efficient management:
- **publicUsersInfo**: Contains less sensitive data (e.g., UUIDs).
- **users**: Stores private user data.
Firebase Authentication ensures secure data access. Real-time updates maintain consistency.

\section{Glossary}
\begin{tabular}{|l|p{10cm}|}
\hline
\textbf{Acronym} & \textbf{Definition} \\ \hline
SDD & Software Design Document \\ \hline
UI & User Interface \\ \hline
UUID & Universally Unique Identifier \\ \hline
API & Application Programming Interface \\ \hline
JS & JavaScript \\ \hline
CSS & Cascading Style Sheets \\ \hline
\end{tabular}

\end{document}

