\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{lipsum}
%Title Info
\title{User Manual}
\author{Group 3}
\date{6 December 2024}
%Page Layout
\geometry{a4paper, margin=1.5in}
\pagestyle{fancy}
\fancyhead[R]{Page \thepage}
\fancyfoot[R]{User Manual}


\begin{document}
\maketitle
\newpage

\section{Objective Breakdown}

\subsection{Purpose}
Want2Remember is a web and mobile application created to help individuals with cognitive challenges manage their daily lives more effectively. It allows users to track and organize important information, including:

\begin{itemize}
\item Memories
\item To-do lists
\item Appointments
\item Contacts
\item Payment details
\end{itemize}

This manual provides an overview of the system’s functionality, design, and architecture to help users understand and use it efficiently.

\subsection{Intended Audience}
This document is tailored for:

\begin{itemize}
\item Professors and students in the California State University, Los Angeles (CSULA) Computer Science department.
\item Employees of We2Link, the group responsible for Want2Remember’s development.
\item End users such as caregivers and individuals with memory-related challenges.
\end{itemize}

\subsection{System Overview}
Want2Remember uses a modular, component-based structure that ensures code reusability and simplifies the application’s complexity. This architecture supports both mobile and web platforms to maximize accessibility and convenience.

\section{Goals and Why It’s Needed}

\subsection{Goals}
Want2Remember aims to assist individuals dealing with memory-related issues, such as:

\begin{itemize}
\item Brain injuries
\item Alzheimer’s disease
\item Other cognitive impairments
\end{itemize}

The application offers customizable templates to log and manage:

\begin{itemize}
\item Memories
\item Passwords
\item To-do lists
\item Medications
\item Appointments
\item Contacts
\end{itemize}

\subsection{Why It’s Needed}
Cognitive impairments can significantly impact a person’s ability to live independently and maintain their quality of life. Want2Remember addresses these challenges by:

\begin{itemize}
\item Promoting independent living
\item Supporting work and educational reintegration
\item Enhancing social interactions and personal safety
\item Facilitating collaboration between caregivers and users
\item Organizing medical and personal records
\end{itemize}

By simplifying daily task management, the app increases user productivity and efficiency, empowering them to lead more structured lives.

\section{How to Access Want2Remember}

\subsection{Access Methods}

\begin{itemize}
\item \textbf{Web Access}: Visit the Want2Remember website. Log in or create an account to start using the application.
\item \textbf{Mobile Access}: Download the Want2Remember app from your device’s app store:
\begin{itemize}
\item \textbf{iOS}: Available on the App Store.
\item \textbf{Android}: Available on the Google Play Store.
\end{itemize}
\end{itemize}

\section*{Conclusion}
Want2Remember provides a user-friendly platform for managing and tracking essential information for those facing cognitive challenges. By addressing both individual and caregiver needs, the application ensures improved organization and quality of life. With ongoing updates and user feedback, Want2Remember is set to remain a reliable and accessible tool for its users.



\end{document}